---
title: "Sidney Island Analysis"
author: "David Hope"
date: "December 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=T)
```

## Outline

This page should provide a guide to follow the analysis presented in *Correlates of annual stopover counts in two species of Arctic-breeding shorebirds: the roles of local, breeding, and climactic drivers.*. You will require the data files included in the \*\*data\_\* folder and you may have to download your own climate indices from the links provided.

## Packages

The analysis requires the following packages:

```{r packages, include=F}
require(tidyverse)
require(cowplot) # Not required but I used it for the plots
require(lme4) # Only for the ageclassModel.r
require(glmmTMB)
library(mgcv)
library(patchwork)
# require(splines)
require(knitr)

library(RNetCDF)
library(gstat)
library(raster)
library(rgdal)
```

These packages are required for specific functions, but don't need to load them.

```{r unloaded-packages, eval=F}
require(DHARMa)


require(car)
require(effects)
require(multcomp)
require(broom.mixed)
require(dotwhisker)
require(bbmle)
require(sjPlot)
```

## Functions and models

Many of the functions used in the analysis are built in separate scripts found in the `R` folder. You should load them before running the analysis.The models I run are described in `R/SI_Climate_Models.r` and the analysis is implemented as a function in `R/RunClimateModels.r`

```{r load-functions, cache=F}
source('R/miscFunctions.r')
source("R/SI_Climate_Models.r")
source("R/RunClimateModels.r")
source("R/CV.r")
```

## 1. Models of Age Class

To import the raw data and run the seasonal patterns in age classes run the following:

```{r age-class, eval=F}
source("ageclassModel.r")
```

It will take some time as CI are generated from bootstrapping.

## 2. Run models of WESA and LESA abundances within and between years

To run the models using the various potential distributions just source the `runModels.r` file. However, if you have done this previously, the model results are stored in `output/model_dist_comparisons.rds`.

```{r run-models, eval=F, include=F}

source("runModels.r")

```

## 3. Analyse the model outputs in AIC and run cross validation.

This will take a while to run together so you can either run the sections from `analyseModels.r` or run the chunks individualy as follows:

```{r read-model-analysis, cache = F}
knitr::read_chunk("analyseModels.r")
```

To run the AIC analysis including tables in Appendix 2

```{r AIC}
```

To run the cross validations that include Tables 1 and 2

```{r CV, eval=F}
```

To check top model assumptions

```{r Assumptions, eval=F}
```

## 4. Generate the plots

First you need to generate the model predictions across the study period:

```{r predictions}
source("generatePredictions.r")
```

Sourcing the following file, should generate all the figures:

```{r figures}
source("Figures.r") 
source("ExtraFigures.R.r") 

```

## Other relavent files

To recreate the non-id analysis mentioned in the manuscript run the following file. It will take a while and may be easier to run in chunks than source:

```{r}
source("non_id_analysis.R")
```


To examine how we ended up with the selected number of knots in the GAM models see `gam_testing.r`.
